Practical Optional Types for Clojure

### 2015-07-10 overview.tex
Fix egregious formatting problems.

\begin{exmp}
\begin{minted}{clj}
  (.getParent (new File "a/b"))  ; :- (U nil Str)
  ;=> "a"
\end{minted}
\label{example:getparent-direct-constructor}
\end{exmp}

@@

\begin{exmp}
\begin{minted}{clojure}
(ann hi [Kw -> Str]) ; interface type for `hi`
(defmulti hi identity) ; dispatch function `identity`
(defmethod hi :en [_] "hello") ; method for `:en`
(defmethod hi :fr [_] "bonjour") ; method for `:fr`
(defmethod hi :default [_] "um...") ; default method
\end{minted}
\label{example:hi-multimethod}
\end{exmp}

>>>>

\begin{exmp}
\begin{minted}{clj}
  ; :- (U nil Str)
  (.getParent (new File "a/b"))  
  ;=> "a"
\end{minted}
\label{example:getparent-direct-constructor}
\end{exmp}

@@

\begin{exmp}
\begin{minted}{clojure}
(ann hi [Kw -> Str]) ; multimethod type
(defmulti hi identity) ; dispatch function `identity`
(defmethod hi :en [_] "hello") ; method for `:en`
(defmethod hi :fr [_] "bonjour") ; method for `:fr`
(defmethod hi :default [_] "um...") ; default method
\end{minted}
\label{example:hi-multimethod}
\end{exmp}
